Project Notes

### 2020-04-05 notes/notes.tex
Notes: update 05/04/2020

\paragraph{04/04/2020 [tomorrow]}
\begin{itemize}
\item
Focus on getting React code generation to work -- 
TicTacToe example for the receive handlers weren't
generalised enough, go back to OneNote to sketch
the encoding before trying it in code.
\end{itemize}

>>>>

\paragraph{05/04/2020}
\begin{itemize}
\item
Implemented templates for React code generation.
The main breakthrough was to better leverage
the type system and reduce duplication in the
generated code. The TicTacToe example had a lot
of duplication by hardcoding the state machine.
The new template pushes the logic to the actual
states and makes the runtime more lightweight.

\item
The generated code for BinaryNoPayload.scr is functional for both Node and browser targets.
\end{itemize}
